### 2016-09-15 doc/manual/version3/inputParameters.tex
added more magnetic drift options

{\ttfamily magneticDriftScheme} = 2: Use the grad-B and curvature drift, plus the parallel velocity correction $v_{\perp}^2/(2 \Omega_c) \vect{b} \vect{b} \cdot \nabla \times \vect{b}$.
}

>>>>

{\ttfamily magneticDriftScheme} = 2: Use the grad-B and curvature
drift, plus the parallel velocity correction $v_{\perp}^2/(2 \Omega_c)
\vect{b} \vect{b} \cdot \nabla \times \vect{b}$.\\

{\ttfamily magneticDriftScheme} = 3: Magnetic drift as defined in
Eq.~(67) in \cite{Kasilov2014}.\\

{\ttfamily magneticDriftScheme} = 4: Magnetic drift as defined in
Eq.~(16) in \cite{Martitsch2016}. (This only works for .bc magnetic
geometry input files so far)\\
